Efficient Calculation of Improved Simultaneous Testing Bands for QQplots with \proglang{R} Package \pkg{qqconf}

### 2021-04-25 article/manuscript.Rnw
changed article to include examples with our code

plot(
  c(1:n) / (n + 1), 
  sort(pvals_scenario_2), 
  type = "l", 
  col = "red", 
  xlab = "Expected Uniform Quantile",
  ylab = "Observed P-value"
)

@@

qq_conf_plot(
  obs = pvals_scenario_2,
  distribution = qunif,
  method = "ell",
  alpha = .05, 
  add = TRUE
)

legend(
  x = .02, 
  y = .95, 
  legend = c("s=20","s=200"), 
  col = c("red","blue"), 
  lty = 1
)
@

@@

<<chisq_qq_log, fig=TRUE, include=FALSE>>=
# Plot 4: Q-Q plot, on the -log10 Scale, of P-values 
# from Chi-Squared Test for Independence in a 2 x 2 Table

plot(
  -log10(bounds$x), 
  -log10(sort(pvals_scenario_2)),
  type = "l",
  col = "red",
  xlab = "-log10(Expected Uniform Quantile)",
  ylab = "-log10(Observed P-value)"
)

# Add the 45-degree line to the plot
lines(-log10(bounds$x), -log10(bounds$x))

# Add the lower bound line for the level .05 
# simultaneous testing bands from equal local levels.
lines(-log10(bounds$x), -log10(bounds$lower_bound))

# Add the upper bound line for the level .05 
# simultaneous testing bands from equal local levels.
lines(-log10(bounds$x), -log10(bounds$upper_bound))

# Add the Q-Q plot for scenario 1, with axes on the -log10 scale.
lines(-log10(bounds$x), -log10(sort(pvals_scenario_1)), col = "blue")

legend(
  x = .2, 
  y = 3, 
  legend = c("s=20", "s=200"), 
  col = c("red","blue"), 
  lty = 1
)
@

>>>>

qq_conf_plot(
  obs = pvals_scenario_2,
  distribution = qunif,
  method = "ell",
  alpha = .05,
  samples_func = lines,
  samples_col = "red"
)

@@

legend(
  "topleft", 
  legend = c("s=20","s=200"), 
  col = c("red","blue"), 
  lty = 1
)
@

@@

<<chisq_qq_log, fig=TRUE, include=FALSE>>=
# Plot 4: Q-Q plot, on the -log10 Scale, of P-values 
# from Chi-Squared Test for Independence in a 2 x 2 Table
n <- 1000

qq_conf_plot(
  obs = pvals_scenario_2,
  distribution = qunif,
  method = "ell",
  alpha = .05,
  samples_func = lines,
  samples_col = "red",
  log10 = TRUE
)

# Add the Q-Q plot for scenario 1.
lines(-log10(c(1:n) / (n + 1)), -log10(sort(pvals_scenario_1)), col = "blue")

legend(
  "topleft",
  legend = c("s=20","s=200"), 
  col = c("red","blue"), 
  lty = 1
)
@

### 2021-04-25 article/manuscript.tex
changed article to include examples with our code

\begin{Schunk}
\begin{Sinput}
R> library(qqconf)
R> n <- 1000
R> bounds <- get_bounds_two_sided(alpha = .05, n = 1000)
R> # Plot 3: Q-Q plot of P-values from Chi-Squared Test
R> # for Independence in a 2 x 2 Table
R> 
R> plot(
+    c(1:n) / (n + 1), 
+    sort(pvals_scenario_2), 
+    type = "l", 
+    col = "red", 
+    xlab = "Expected Uniform Quantile",
+    ylab = "Observed P-value"
+  )
R> # Add the Q-Q plot for scenario 1.
R> lines(c(1:n) / (n + 1), sort(pvals_scenario_1), col = "blue")
R> qq_conf_plot(
+    obs = pvals_scenario_2,
+    distribution = qunif,
+    method = "ell",
+    alpha = .05, 
+    add = TRUE
+  )
R> legend(
+    x = .02, 
+    y = .95, 
+    legend = c("s=20","s=200"), 
+    col = c("red","blue"), 
+    lty = 1
+  )
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> # Plot 4: Q-Q plot, on the -log10 Scale, of P-values 
R> # from Chi-Squared Test for Independence in a 2 x 2 Table
R> 
R> plot(
+    -log10(bounds$x), 
+    -log10(sort(pvals_scenario_2)),
+    type = "l",
+    col = "red",
+    xlab = "-log10(Expected Uniform Quantile)",
+    ylab = "-log10(Observed P-value)"
+  )
R> # Add the 45-degree line to the plot
R> lines(-log10(bounds$x), -log10(bounds$x))
R> # Add the lower bound line for the level .05 
R> # simultaneous testing bands from equal local levels.
R> lines(-log10(bounds$x), -log10(bounds$lower_bound))
R> # Add the upper bound line for the level .05 
R> # simultaneous testing bands from equal local levels.
R> lines(-log10(bounds$x), -log10(bounds$upper_bound))
R> # Add the Q-Q plot for scenario 1, with axes on the -log10 scale.
R> lines(-log10(bounds$x), -log10(sort(pvals_scenario_1)), col = "blue")
R> legend(
+    x = .2, 
+    y = 3, 
+    legend = c("s=20", "s=200"), 
+    col = c("red","blue"), 
+    lty = 1
+  )
\end{Sinput}
\end{Schunk}

>>>>

\begin{Schunk}
\begin{Sinput}
R> library(qqconf)
R> n <- 1000
R> bounds <- get_bounds_two_sided(alpha = .05, n = 1000)
R> # Plot 3: Q-Q plot of P-values from Chi-Squared Test
R> # for Independence in a 2 x 2 Table
R> 
R> 
R> qq_conf_plot(
+    obs = pvals_scenario_2,
+    distribution = qunif,
+    method = "ell",
+    alpha = .05,
+    samples_func = lines,
+    samples_col = "red"
+  )
R> # Add the Q-Q plot for scenario 1.
R> lines(c(1:n) / (n + 1), sort(pvals_scenario_1), col = "blue")
R> legend(
+    "topleft", 
+    legend = c("s=20","s=200"), 
+    col = c("red","blue"), 
+    lty = 1
+  )
\end{Sinput}
\end{Schunk}

@@

\begin{Schunk}
\begin{Sinput}
R> # Plot 4: Q-Q plot, on the -log10 Scale, of P-values 
R> # from Chi-Squared Test for Independence in a 2 x 2 Table
R> n <- 1000
R> qq_conf_plot(
+    obs = pvals_scenario_2,
+    distribution = qunif,
+    method = "ell",
+    alpha = .05,
+    samples_func = lines,
+    samples_col = "red",
+    log10 = TRUE
+  )
R> # Add the Q-Q plot for scenario 1.
R> lines(-log10(c(1:n) / (n + 1)), -log10(sort(pvals_scenario_1)), col = "blue")
R> legend(
+    "topleft",
+    legend = c("s=20","s=200"), 
+    col = c("red","blue"), 
+    lty = 1
+  )
\end{Sinput}
\end{Schunk}
